Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

### 2022-03-30 Codes/PrepareResults.rmd
correct some errors and modified our replies to the editor

```{r set-up, cache = F}
library(knitr)
library(here)

here::i_am("GitControlled/Writing/manuscript_cea.rmd")

knitr::opts_chunk$set(
  # cache = TRUE
  cache = FALSE
)
```
```{r packages, cache = FALSE, include = FALSE}
# === packages ===#
# --- data wrangling--- #
library(sf)
library(data.table)
library(tidyverse)

@@

vis_all_points <- rbind(vis_res_pred, vis_true_points)

@@

field_m_error_high <-
  ggplot(field_cell_high_sf) +
    geom_sf(aes(fill = yield_error), size = 0) +
    scale_fill_viridis_c() +
    labs(fill = expression(paste( ~ epsilon, " (kg/ha)"))) +
    ggtitle("(2) High error") +
    theme_figure
```

@@

# === Table creation === #
report_summary_res_CNN_RF_BRF <-
  summary_res_CNN_RF_BRF %>%
  flextable(.) %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Model = "Model",
    blank1 = "", count_y_RF = "RF", count_RF = "RF",
    blank2 = "", count_y_BRF = "BRF", count_BRF = "BRF",
    blank3 = "", count_y_CNN = "CNN", count_CNN = "CNN",
    blank4 = "", Total = "Total #YP",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(3:4, 6:7, 9:10), part = "header") %>%
  add_header(
    Model = "",
    blank1 = "", count_y_RF = "#Y", count_RF = "#YP",
    blank2 = "", count_y_BRF = "#Y", count_BRF = "#YP",
    blank3 = "", count_y_CNN = "#Y", count_CNN = "#YP",
    blank4 = "", Total = "",
    top = FALSE
  ) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  footnote(
    value = as_paragraph("NOTE: #Y indicates the number of simulation rounds in which the model provided the lowest RMSE for yield prediction. #YP indicates the number of simulation rounds in which the model provided the lower RMSE of yield prediction and the highest profit at the same time."),
    ref_symbols = NA
  ) %>%
  # set_table_properties(width = .7, layout = "autofit") %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(3:4, 6:7, 9:10), width = 0.6) %>%
  width(j = 12, width = 0.82) %>%
  width(j = 1, width = 0.5) %>%
  width(j = c(2, 5, 8, 11), width = 0.1)
```

@@

```{r}
# === Load the data === #
Simres_low <- 
  here("Shared/Results/for_writing/allML_summary_bySim_low.rds") %>%
  readRDS()

@@

Simres_low_high<-
 bind_rows(Simres_low, Simres_high, .id = "Degree") %>%
 .[, Degree := ifelse(Degree==1, "Low", "High")] %>%
 .[, Degree := factor(Degree, levels =c("Low", "High"))] %>%
 .[type == "test",]

@@

# === Summary Table (Testing Data sets) === #
table_optN_low_high <- 
  table_optN_prep_low_high %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  as_grouped_data(, groups = c("Degree")) %>%
  flextable() %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Degree = "Error Size",
    Model = "Model",
    blank1 = "", rmse_optN_RF = "RF", pi_loss_RF = "RF",
    blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
    blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
    blank3 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(4:5, 7:8, 10:11, 13:14), part = "header") %>%
  add_header(
    Degree = "",
    Model = "",
    blank1 = "", rmse_optN_RF = "RMSE", pi_loss_RF = "pi_loss",
    blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
    blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
    blank3 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
    top = FALSE
  ) %>%
  compose(i = 2, j = c(5, 8, 11, 14), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  width(j = c(2,5,8,11, 14), width=0.3) %>%
  footnote(
    # i = 1, j = c(4, 7, 10, 13), part = "header",
    value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level. The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), "."),
    ref_symbols = NA
  ) %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(4, 5, 7, 8, 10, 11, 13, 14), width = 0.6) %>%
  width(j = 1, width = 0.82) %>%
  width(j = 2, width = 0.5) %>%
  align(j = 2, align = "left", part = "body") %>%
  width(j = c(3, 6, 9, 12), width = 0.1)
```

@@

```{r}
# /*--------------------------------*/
#' ## Yield prediction
#/*--------------------------------*/ 
report_table_y_low_high <-
  Simres_low_high %>%
  .[, .(rmse_y = mean(rmse_y)), by = .(Degree, Method, Model)] %>%
  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
  dcast(Degree + Model ~ Method, value.var = "rmse_y") %>%
  .[, CF_base := "-"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  as_grouped_data(, groups = c("Degree")) %>%
  flextable(.) %>%
  set_header_labels(values = list(
    Degree = "Error Size",
    Model = "Model",
    RF = "RF",
    BRF = "BRF",
    CNN = "CNN",
    CF_base = "CF-base"
  )) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  #- change the borders just for consistency with other figures -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  autofit() %>%
  width(j = 1, width = 0.82) %>%
  align(j = 2, align = "left", part = "body") 
```

@@

# === Table creation === #
count_tbl_low_high <-
  prepare_count_tbl_low_high %>%
  as_grouped_data(, groups = c("Degree")) %>%
  flextable(.) %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Degree = "Error Size",
    Model = "Model",
    blank1 = "", count_y_RF = "RF", count_RF = "RF",
    blank2 = "", count_y_BRF = "BRF", count_BRF = "BRF",
    blank3 = "", count_y_CNN = "CNN", count_CNN = "CNN",
    blank4 = "", Total = "Total #YP",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(4:5, 7:8, 10:11), part = "header") %>%
  add_header(
    Degree = "",
    Model = "",
    blank1 = "", count_y_RF = "#Y", count_RF = "#YP",
    blank2 = "", count_y_BRF = "#Y", count_BRF = "#YP",
    blank3 = "", count_y_CNN = "#Y", count_CNN = "#YP",
    blank4 = "", Total = "",
    top = FALSE
  ) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  footnote(
    value = as_paragraph("NOTE: #Y indicates the number of simulation rounds in which the model provided the lowest RMSE for yield prediction. #YP indicates the number of simulation rounds in which the model provided the lower RMSE of yield prediction and the highest profit at the same time."),
    ref_symbols = NA
  ) %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(4:5, 7:8, 10:11), width = 0.6) %>%
  width(j = 1, width = 0.82) %>%
  width(j = 13, width = 0.82) %>%
  width(j = 2, width = 0.5) %>%
  align(j = 2, align = "left", part = "body") %>%
  width(j = c(3, 6, 9, 12), width = 0.1)

>>>>

```{r packages, cache = FALSE, include = FALSE}
# === packages ===#
# --- data wrangling--- #
library(sf)
library(data.table)
library(tidyverse)

@@

vis_all_points <- rbind(vis_res_pred, vis_true_points)
```

@@

field_m_error_high <-
  ggplot(field_cell_high_sf) +
  geom_sf(aes(fill = yield_error), size = 0) +
  scale_fill_viridis_c() +
  labs(fill = expression(paste(~epsilon, " (kg/ha)"))) +
  ggtitle("(2) High error") +
  theme_figure
```

@@

# === Table creation === #
report_summary_res_CNN_RF_BRF <-
  summary_res_CNN_RF_BRF %>%
  flextable(.) %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Model = "Model",
    blank1 = "", count_y_RF = "RF", count_RF = "RF",
    blank2 = "", count_y_BRF = "BRF", count_BRF = "BRF",
    blank3 = "", count_y_CNN = "CNN", count_CNN = "CNN",
    blank4 = "", Total = "Total #YP",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(3:4, 6:7, 9:10), part = "header") %>%
  add_header(
    Model = "",
    blank1 = "", count_y_RF = "#Y", count_RF = "#YP",
    blank2 = "", count_y_BRF = "#Y", count_BRF = "#YP",
    blank3 = "", count_y_CNN = "#Y", count_CNN = "#YP",
    blank4 = "", Total = "",
    top = FALSE
  ) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  footnote(
    value = as_paragraph("NOTE: #Y indicates the number of simulation rounds in which the model provided the lowest RMSE for yield prediction. #YP indicates the number of simulation rounds in which the model provided the lower RMSE of yield prediction and the highest profit at the same time."),
    ref_symbols = NA
  ) %>%
  # set_table_properties(width = .7, layout = "autofit") %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(3:4, 6:7, 9:10), width = 0.6) %>%
  width(j = 12, width = 0.82) %>%
  width(j = 1, width = 0.8) %>%
  width(j = c(2, 5, 8, 11), width = 0.1)
```

@@

```{r, cache = F}
# === Load the data === #
Simres_low <-
  here("Shared/Results/for_writing/allML_summary_bySim_low.rds") %>%
  readRDS()

@@

Simres_low_high <-
  bind_rows(Simres_low, Simres_high, .id = "Degree") %>%
  .[, Degree := ifelse(Degree == 1, "Low", "High")] %>%
  .[, Degree := factor(Degree, levels = c("Low", "High"))] %>%
  .[type == "test", ]

@@

# === Summary Table (Testing Data sets) === #
table_optN_low_high <-
  table_optN_prep_low_high %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  as_grouped_data(, groups = c("Degree")) %>%
  flextable() %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Degree = "Error Size",
    Model = "Model",
    blank1 = "", rmse_optN_RF = "RF", pi_loss_RF = "RF",
    blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
    blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
    blank3 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(4:5, 7:8, 10:11, 13:14), part = "header") %>%
  add_header(
    Degree = "",
    Model = "",
    blank1 = "", rmse_optN_RF = "RMSE", pi_loss_RF = "pi_loss",
    blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
    blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
    blank3 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
    top = FALSE
  ) %>%
  compose(i = 2, j = c(5, 8, 11, 14), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  width(j = c(2, 5, 8, 11, 14), width = 0.3) %>%
  footnote(
    # i = 1, j = c(4, 7, 10, 13), part = "header",
    value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level. The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")), "."),
    ref_symbols = NA
  ) %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(4, 7, 10, 13), width = 0.6) %>%
  width(j = c(5, 8, 11, 14), width = 0.5) %>%
  width(j = 2, width = 0.7) %>%
  align(j = 2, align = "left", part = "body") %>%
  width(j = c(3, 6, 9, 12), width = 0.05)
```

@@

```{r}
# /*--------------------------------*/
#' ## Yield prediction
# /*--------------------------------*/
report_table_y_low_high <-
  Simres_low_high %>%
  .[, .(rmse_y = mean(rmse_y)), by = .(Degree, Method, Model)] %>%
  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
  dcast(Degree + Model ~ Method, value.var = "rmse_y") %>%
  .[, CF_base := "-"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  as_grouped_data(, groups = c("Degree")) %>%
  flextable(.) %>%
  set_header_labels(values = list(
    Degree = "Error Size",
    Model = "Model",
    RF = "RF",
    BRF = "BRF",
    CNN = "CNN",
    CF_base = "CF-base"
  )) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  #- change the borders just for consistency with other figures -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  autofit() %>%
  width(j = 1, width = 0.82) %>%
  align(j = 2, align = "left", part = "body")
```

@@

# === Table creation === #
count_tbl_low_high <-
  prepare_count_tbl_low_high %>%
  as_grouped_data(, groups = c("Degree")) %>%
  flextable(.) %>%
  border_remove() %>%
  delete_part(part = "header") %>%
  add_header(
    Degree = "Error Size",
    Model = "Model",
    blank1 = "", count_y_RF = "RF", count_RF = "RF",
    blank2 = "", count_y_BRF = "BRF", count_BRF = "BRF",
    blank3 = "", count_y_CNN = "CNN", count_CNN = "CNN",
    blank4 = "", Total = "Total #YP",
    top = TRUE
  ) %>%
  merge_h(part = "header") %>%
  hline_bottom(j = c(4:5, 7:8, 10:11), part = "header") %>%
  add_header(
    Degree = "",
    Model = "",
    blank1 = "", count_y_RF = "#Y", count_RF = "#YP",
    blank2 = "", count_y_BRF = "#Y", count_BRF = "#YP",
    blank3 = "", count_y_CNN = "#Y", count_CNN = "#YP",
    blank4 = "", Total = "",
    top = FALSE
  ) %>%
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  footnote(
    value = as_paragraph("NOTE: #Y indicates the number of simulation rounds in which the model provided the lowest RMSE for yield prediction. #YP indicates the number of simulation rounds in which the model provided the lower RMSE of yield prediction and the highest profit at the same time."),
    ref_symbols = NA
  ) %>%
  fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
  autofit() %>%
  width(j = c(4:5, 7:8, 10:11), width = 0.5) %>%
  width(j = 13, width = 0.82) %>%
  width(j = 2, width = 0.7) %>%
  align(j = 2, align = "left", part = "body") %>%
  width(j = c(3, 6, 9, 12), width = 0.05)
```

### 2022-03-30 Writing/CEA_3rd_round/replies_rev.rmd
minor edit
correct some errors and modified our replies to the editor

We actually realized the results presented in Figure 6 (in the previous round) is completely invalid. As you pointed out the problem with the relationship presented in the figure is basically comparing apples and oranges: comparing across simulation rounds. Figure 8 plots RMSE of yield and EONR predictions by model and simulation round for several simulation rounds. Figure 6 in the previous round was basically mixing RMSE from all the simulation rounds and finding $R^2$ of the two relationship. That is why $R^2$ was extremely low. Therefore, we decided to remove the figure entirely. Also, we no longer claim that yield and EONR predictions are not correlated at all as we realized that it is false. Thank you so much for saving us from claiming the false statement.

However, please note that our claim that better yield prediction does "not necessarily" lead to higher profit remains intact. According to your suggestions, we provide much more in-depth discussions about why that is the case under section 4.2. As you suggested, models that can recover the "structure" of the yield response function will perform well in predicting EONR. However, you can predict yield levels at the observed rates (rates that are actually applied in the experiment) without recovering the structure of the yield response function well (predicting yield levels well for wrong reasons). The training process of prediction-oriented ML methods may twist the reasonings of why yield varies in a way that sacrifices its ability to recover yield response function as long as it fits its primary objective of predicting yield levels well at the "observed" nitrogen rate for each site well. Please see our more detailed discussions on this matter in section 4.2.

We understand your suggestion of running simulations under different magnitude of error comes from your doubt about why yield and EONR prediction is not correlated. But, we conducted simulations with different degrees of error anyway. **The results are shown in Appendix G**.

@@

<span style="color:blue">  
We already discuss our results to the state of the art of the literature. The state of the art is sadly trying to predict yields site-specifically as well as possible. We show that such practice can be misleading and economically harmful when your ultimate goal is to actually help farmers make nitrogen application decisions (predicting EONR well). There is nothing wrong with our approach in yield prediction as evident in Figure E.1<!-- Figure 12 -->. We are using ML methods that have been used in the literature of OFE for site-specific input management. Those studies were published very recently. We added our description about how the size of epsilon affects our results briefly in Appendix G. But, it is important to realize that all the models uses the same data in our study. That is, the models are competing against each other on the level ground. Changing the size of error has little effects on the comparative advantage of CF over other models much.

>>>>

We actually realized the results presented in Figure 6 (in the previous round) is completely invalid. As you pointed out the problem with the relationship presented in the figure is basically comparing apples and oranges: comparing across simulation rounds. Figure 8 plots RMSE of yield and EONR predictions by model and simulation round for several simulation rounds. Figure 6 in the previous round was basically mixing RMSE from all the simulation rounds and finding $R^2$ of the two relationship. That is why $R^2$ was extremely low. Therefore, we decided to remove the figure entirely. Also, we no longer claim that yield and EONR predictions are not correlated at all as we realized that it is false. Thank you so much for saving us from claiming the false statement. We conducted simulations with different degrees of error according to your suggestion. **The results are shown in Appendix G**. By looking at Tables 1, 3, G.1, and G.3, you can see that as the error size decreases, both yield and EONR RMSEs decrease. So, in this sense, yield and EONR predictions are indeed correlated as expected.

However, our claim that the models with the highest yield prediction power is not necessarily the best EONR prediciton (or the most profitable) model remains valid. Please note that this claim comes from comparisons **across the models** given the **same** dataset (so the same errors). Since we consider this a very important point for researchers in this field, we now provide much more in-depth discussions about why that is the case under section 4.2. As you suggested, models that can recover the "structure" of the yield response function will perform well in predicting EONR. However, you can predict yield levels at the observed rates (rates that are actually applied in the experiment) without recovering the structure of the yield response function well (predicting yield levels well for wrong reasons). The training process of prediction-oriented ML methods may twist the reasonings of why yield varies in a way that sacrifices its ability to recover yield response function as long as it fits its primary objective of predicting yield levels well at the "observed" nitrogen rate for each site well. Please see our more detailed discussions on this matter in section 4.2.

@@

<span style="color:blue">  
We already discuss our results to the state of the art of the literature. The state of the art is sadly trying to predict yields site-specifically as well as possible. We show that such practice can be misleading and economically harmful when your ultimate goal is to actually help farmers make nitrogen application decisions (predicting EONR well). There is nothing wrong with our approach in yield prediction as evident in Figure E.1<!-- Figure 12 -->. We are using ML methods that have been used in the literature of OFE for site-specific input management. Those studies were published very recently. We added our description about how the size of epsilon affects our results briefly in Appendix G. We added the following at line xx page yy:

"Finally, the simulation results at a smaller and larger size of the error term are presented in Appendix G as a sensitivity check for interested readers. Basically, qualitative results remain the same."

### 2022-03-30 Writing/appendix.rmd
correct some errors and modified our replies to the editor

## Appendix G: Simulations with Different Size of Yield Disturbance Term.
In this section, we present the results of EONR estimation and yield prediction with different size of random yield error ($\varepsilon$). We created two additional yield datasets	that are only different in the size of $\varepsilon$ from the yield datasets we used in the study by changing the variogram parameter of $psill$ for $r^{\varepsilon}_{i,j}$. Half size of $psill$ value ($0.0075$) was used to create yield datasets with low yield error, and one and a half size of $psill$ value ($$0.0225$$) was used to create yield datasets with high yield error. Figure G.1 illustrates examples of the generated low and high $\varepsilon$.

```{r fig-nExp-yield, fig.width=7, fig.height=6, fig.cap = "Figure G.1: An example of experimental design of N and generated yield at the subplot resolution"}
field_m_error_low | field_m_error_high
```

>>>>

## Appendix G: Simulations with Different Size of Yield Disturbance Term.
In this section, we present the results of EONR estimation and yield prediction with different size of random yield error ($\varepsilon$). We created two additional yield datasets	that are only different in the size of $\varepsilon$ from the yield datasets we used in the study by changing the variogram parameter of $psill$ for $r^{\varepsilon}_{i,j}$. Half size of $psill$ value ($0.0075$) was used to create yield datasets with low yield error, and one and a half size of $psill$ value ($0.0225$) was used to create yield datasets with high yield error. Figure G.1 illustrates examples of the generated low and high $\varepsilon$.

```{r fig-nExp-yield, fig.width=7, fig.height=6, fig.cap = "Figure G.1: An example of experimental design of N and generated yield at the subplot resolution", cache = TRUE}
field_m_error_low | field_m_error_high
```

### 2022-03-30 Writing/manuscript_cea.rmd
correct some errors and modified our replies to the editor

opts_chunk$set(
  fig.align = "center",
  fig.retina = 5,
  warning = F,
  message = F,
  cache = T,
  echo = F
)
```

```{r, cache = FALSE}
# === packages ===#
library(tidyverse)
library(data.table)
library(sf)
library(png)
library(RColorBrewer)
library(patchwork)
library(plotly)
library(magrittr)
library(ggplot2)
library(viridis)
library(tmap)
library(ggthemes)
library(mgcv)
library(ggpubr)
library(flextable)
library(officer)
library(officedown)
library(modelsummary)
library(raster)
library(bookdown)
library(png)
library(grid)
library(causalTree)
library(rpart)
library(rattle)
```

```{r analyses, results = "hide", fig.show='hide', cache = FALSE}
# /*=================================================*/
#' # Create figures and tables
# /*=================================================*/
# --- Convert an Rmd file into a pure R file using purl() ---#
knitr::purl(
  here("GitControlled/Codes/PrepareResults.rmd"),
  output = here("GitControlled/Codes/PrepareResults.R")
)

# --- Read the simulation results and prepare figures and tables ---#
source(here("GitControlled/Codes/PrepareResults.R"))
```

>>>>

opts_chunk$set(
  fig.align = "center",
  fig.retina = 5,
  warning = F,
  message = F,
  cache = F,
  echo = F
)
```

```{r, cache = FALSE}
# === packages ===#
library(tidyverse)
library(data.table)
library(sf)
library(png)
library(RColorBrewer)
library(patchwork)
library(plotly)
library(magrittr)
library(ggplot2)
library(viridis)
library(tmap)
library(ggthemes)
library(mgcv)
library(ggpubr)
library(flextable)
library(officer)
library(officedown)
library(modelsummary)
library(raster)
library(bookdown)
library(png)
library(grid)
library(causalTree)
library(rpart)
library(rattle)
```
```{r, include = F, cache = F}
knit_child(here("GitControlled/Codes/PrepareResults.Rmd"), quiet = TRUE)
```
